Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
fix idea of proof refs

Next, part (b) immediately follows from an application of Lemma ~\ref{relations_from_generators_induction}, we only need verify the hypotheses of Lemma ~\ref{relations_from_generators_induction}. The first two hypotheses follow immediately from the construction of block order. Checking the third condition is quite technical, but the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***} give certain slope conditions, which are precisely what is needed to verify the third condition of Lemma ~\ref{relations_from_generators_induction}.

>>>>

Next, part (b) immediately follows from an application of Lemma ~\ref{lem:relations_from_generators_induction}, we only need verify the hypotheses of Lemma ~\ref{lem:relations_from_generators_induction}. The first two hypotheses follow immediately from the construction of block order. Checking the third condition is quite technical, but the conditions ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***} give certain slope conditions, which are precisely what is needed to verify the third condition of Lemma ~\ref{lem:relations_from_generators_induction}.
